Increased productivity using Atomify - a real-time LAMMPS visualizer

### 2018-06-12 ms.tex
Updated figure to reflect new script

\section{\label{sec:casestudy}Case study: flow through a narrow nanotube}
The features of Atomify is best demonstrated through a case study where many of the features are useful to be productive in the script development.
We have chosen to create a system with fluid flow inside a tight nanochannel.
This involves creating a somewhat complicated initial geometry with multiple regions where we apply different rules such as a dissipative thermostat, constant force mimicking applied pressure gradient and frozen atoms to avoid net momentum of the solid.

>>>>

\section{\label{sec:casestudy}Case study: flow through a narrow nanotube}
The features of Atomify is best demonstrated through a case study where many of
them are useful to obtain a productive workflow during script development.
We have chosen to create a system with fluid flow inside a tight nanochannel.
This involves creating a somewhat complicated initial geometry with multiple regions
where we apply different rules such as a dissipative thermostat, constant force mimicking
applied pressure gradient and frozen atoms to avoid net momentum of the solid.
